### 2023-05-04 Documentation/UFMG/PFCII/systemDescription/systemDescription.tex
documentation

\chapter[System Description]{System Description}
\label{chap:system_description}

In this chapter, we will discuss the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library \cite{Monica}.

@@

    Wireless communication allows us to make measurements disconnected to an external power supply, which gives us more safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
    The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
    TiePie WifiScope WS6 has a resolution of up to 16 bit at a minimal input range of 200 mV, sufficient to measure currents down to 1 nA.

@@

  The pump integration in the automation algorithm brings us a new controllable variable, the Flow rate. Now we can control the spraying mode with the
  two main variables that affect the system. 
  It will bring more complexity for the system since now we are dealing with multivariable control.
  Controlling also the flow rate gives to this project a new dimension in the system giving us freedom to explore the flow rate properties.
  With this new input variable our control is a MISO (Multiple Inputs Single Output) system.

  About the pump interface. As I could not find a good ready-to-use library for this pump I developed a simple and intuitive interface to be our software routine.
  The communication protocol used is RS-232. In the software routine the communication used is python serial interface. The pump commands list were found in the user manual.

  % The supply at constant pressure can also favor the stability of the spray\cite{prunet}. However, the flow rate depends on the applied pressure and pressure losses between the tank and the end of the capillary, which themselves are dependent on the liquid chosen and on its temperature. This volume flow rate may also depend on the applied voltage, since the electrostatic pressure on the meniscus produces a suction effect.

@@

        To conclude, json files are good as a system output because of its human readability. But as the database gets bigger json becomes to be a slow to read and heavy way to store the data. For that, saving the data frame in a compressed type of file called feather is much faster to work with the data.

@@

    In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software. 
    Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.

    \begin{figure}[H]
      \centering
      \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
      \caption{EHDA automation system setup}
      \label{fig:Methodology_example1}
  \end{figure}
\clearpage

>>>>

\chapter{System Description}
\label{chap:system_description}

In this chapter, we will discuss the equipment used in detail, including its integration and how it was modeled and implemented in both hardware and software. 
The python automation routine that is the focus of this project was started by a previous student\cite{Monica}, and the software itself was originally created as an electrospray multipurpose library.

@@

    Wireless communication allows us to make measurements disconnected to an external power supply, which increase safety when using high voltage potential references and also reduce the signal noise collected from external power lines.
    The current is routed directly via the input, hence the oscilloscope measures the voltage dropped via its input resistance (which can be switched between 1 or 2 Mohms).
    TiePie WifiScope WS6 has a resolution of up to 16 bit at a minimal input range of 200 mV, sufficient to measure currents down to 1 nA.

@@

  The pump integration in the automation algorithm was done in this work, bringing us a new controllable variable, the flow rate. We can control the spraying mode with the
  two main variables that affect the system. 
  It brings more complexity for the system since now we are dealing with multivariable control.
  Controlling also the flow rate gives to this project a new dimension in the system giving us freedom to explore the flow rate properties.
  With this new input variable our control is a MISO (Multiple Inputs Single Output) system.

  About the pump interface, as there was no good ready-to-use library, I developed a simple and intuitive interface to be used in our software routine.
  The communication protocol used is RS-232 and the pump commands list were found in the user manual.

@@

        To conclude, json files are good as a system output because of its human readability. But as the database gets bigger json becomes to be a slow to read and heavy to store data. For that, saving the data frame in a compressed type of file called feather is much faster to work with it.

@@

    In this chapter we described the system description detailing the hardware instruments, how it was modelled and its implementation in the software. 
  %   Figure \ref{fig:Methodology_example1} shows a print screen of the system being used.

  %   \begin{figure}[H]
  %     \centering
  %     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
  %     \caption{EHDA automation system setup}
  %     \label{fig:Methodology_example1}
  % \end{figure}

\clearpage
